method

### 2021-08-26 06_Paper/ER-ED/method.Rmd
added text
each sentence on one line

## 2.1 Power analysis and participants

xxx.

@@

All session took place in a shielded cabin with constant lighting. Participants received information about the

>>>>

## 2.1 Participants

Participants

@@

The study consisted of two sessions, one week apart. 
Both sessions took place in a shielded cabin with constant lighting. 
Before each session, participants received information about the respective experimental procedure and signed informed consent. 
At the beginning of the first session participants filled out a demographic questionnaire. 
Afterwards the completed an n-Back task
